### 2016-01-21 AcademicPaperSummaries/PaperSummaries.tex
Updated with Ryan (2011)

>>>>

\textbf{Ryan, John Barry. ``Social networks as a shortcut to correct voting.'' American Journal of Political Science 55.4 (2011): 753-766. APA}\\
Ryan presents the results of an experiment about how people use information from their social network to determine which of several candidates is likely to best represent their interests. The motivation is a gap between the predictions of formal theory, which predicts that listeners should judge the credibility of messengers according to their individual merits, and the \textit{autoregressive influence theory} that proposes that speakers are influential to the degree that their messages conform to the other messages that the voter is receives (or accepts?). \underline{Implied Mechanism:} The paper tests the salience mechanism, in which messages from other actors, with potentially divergent preferences, influences how actors weigh their decisions.

The experiment is set up so that individuals decide on one of two computer-generated candidates to vote for. There are three types of voters: 1) control group has no contacts with other players while the treatment group exchanges messages; 2) partisan voters get extra benefits if their candidate wins, independent voters are indifferent; 3) informed voters get extra information about the non-partisan benefits of each candidate. The \textit{results} are consistent with the predictions of the autoregressive influence theory: uninformed voters benefited from having social information, informed subjects were harmed unless they were primarily contacted by people with the same preferences that they had. People tended to vote as their social networks voted. The magnitude of the effects seems very small.

\section{Terrorism}

\textbf{de Mesquita, Ethan Bueno. "The political economy of terrorism: A selective overview of recent work." The Political Economist 10.1 (2008): 1-12.
APA} (Week one)

This is a literature review essay about the then-current strand of the literature of academic study of terrorism, with a particular focus on the outcomes of formal models.
